MINOS Handover Plots

### 2023-12-14 minos/validation/handovers.Rmd
Adding poverty metrics to handovers

```{r}
start.year <- 2021
save.path <- here::here("plots", "handovers", 'default')
create.if.not.exists(save.path)

@@

## S7 Labour State

```{r}
prepped.list <- validation_prep_ordinal(raw.dat, base.dat, 'S7_labour_state')

lab.state <- prepped.list$var
lab.state.norm <- prepped.list$norm

# Now plot
ggplot(data = lab.state, mapping = aes(x = time, y = n, group = S7_labour_state, colour = S7_labour_state)) +
  geom_line() +
  geom_vline(xintercept=start.year, linetype='dotted') +
  labs(title = 'S7 Labour State', subtitle = 'Counts by Level') +
  xlab('Year') +
  ylab('Count')

ggplot(data = lab.state.norm, mapping = aes(x = time, y = prct, fill=S7_labour_state)) +
  geom_bar(stat = 'identity') +
  geom_vline(xintercept=start.year, linetype='dotted') +
  labs(title = 'S7 Labour State') +
  xlab('Year') +
  ylab('Proportion')

if (shall.we.save) {
  ggsave(filename = 'S7_labour_state.png',
         plot = last_plot(),
         path = save.path)
}

rm(prepped.list, lab.state, lab.state.norm)
```

```{r}
pivoted <- combine_and_pivot_long(df1 = base.dat, 
                                       df1.name = 'simulated', 
                                       df2 = raw.dat, 
                                       df2.name = 'raw', 
                                       var = 'S7_labour_state')

cv_ordinal_plots(pivoted.df = pivoted, 
                 var = 'S7_labour_state',
                 save = shall.we.save,
                 save.path = save.path)
```

## Child Ages

```{r}
base.child.ages <- base.dat %>%
  dplyr::select(pidp, hidp, time, "child_ages", "nkids") %>%
  filter(time > 2009) %>%
  group_by(time, hidp) %>%
  summarise(child_ages = find_mode(child_ages))

s<- strsplit(base.child.ages$child_ages, "_")

base.child.ages.expanded <- data.frame(time = rep(base.child.ages$time, sapply(s, length)), expanded_child_ages = unlist(s))
base.child.ages.expanded <- base.child.ages.expanded %>%
  group_by(time, expanded_child_ages) %>%
  summarise(age_counts = n())

ggplot(data = base.child.ages.expanded, mapping = aes(x = time, y = age_counts, group = expanded_child_ages, colour =  factor(as.numeric(expanded_child_ages)))) +
  geom_line() +
  labs(title = "Child Age Counts Over Time", subtitle = 'Counts by Level') +
  scale_colour_viridis_d() +
  xlab('Year') +
  ylab('Count')

ggplot(data = base.child.ages.expanded, mapping = aes(x = factor(as.numeric(expanded_child_ages)), y = age_counts, group = factor(time), colour = factor(time))) +
  geom_line() +
  labs(title = "Child Age Counts Over Time", subtitle = 'Counts by Level') +
  scale_colour_viridis_d() +
  xlab('Year') +
  ylab('Count')

base.child.ages.nkids <- base.dat %>%
  group_by(time, hidp) %>%
  summarise(nkids_counts = mean(nkids)) %>%
  group_by(time) %>%
  summarise(nkids_by_year = sum(nkids_counts))

ggplot(data = base.child.ages.nkids, mapping = aes(x = time, y = nkids_by_year)) +
  geom_line() +
  labs(title = "nkids Count Over Time", subtitle = 'Counts by Level') +
  xlab('Year') +
  ylab('Count')

@@

>>>>

```{r}
start.year <- 2020
save.path <- here::here("plots", "handovers", 'default')
create.if.not.exists(save.path)

@@

## Poverty

### Absolute poverty

```{r}
prepped.list <- validation_prep_ordinal(raw.dat, base.dat, 'absolute_poverty')

tit <- 'Absolute Poverty'

# Now plot
ggplot(data = var, mapping = aes(x = time, y = n, group = absolute_poverty, colour = absolute_poverty)) +
  geom_line() +
  geom_vline(xintercept=start.year, linetype='dotted') +
  labs(title = tit, subtitle = 'Counts by Level') +
  xlab('Year') +
  ylab('Count')

ggplot(data = norm, mapping = aes(x = time, y = prct, fill=absolute_poverty)) +
  geom_bar(stat = 'identity') +
  geom_vline(xintercept=start.year, linetype='dotted') +
  labs(title = tit) +
  xlab('Year') +
  ylab('Proportion')

if (shall.we.save) {
  ggsave(filename = 'absolute_poverty.png',
         plot = last_plot(),
         path = save.path)
}

### Relative poverty

```{r}
prepped.list <- validation_prep_ordinal(raw.dat, base.dat, 'relative_poverty')

tit <- 'Relative Poverty'

# Now plot
ggplot(data = var, mapping = aes(x = time, y = n, group = relative_poverty, colour = relative_poverty)) +
  geom_line() +
  geom_vline(xintercept=start.year, linetype='dotted') +
  labs(title = tit, subtitle = 'Counts by Level') +
  xlab('Year') +
  ylab('Count')

ggplot(data = norm, mapping = aes(x = time, y = prct, fill=relative_poverty)) +
  geom_bar(stat = 'identity') +
  geom_vline(xintercept=start.year, linetype='dotted') +
  labs(title = tit) +
  xlab('Year') +
  ylab('Proportion')

if (shall.we.save) {
  ggsave(filename = 'relative_poverty.png',
         plot = last_plot(),
         path = save.path)
}

### Persistent poverty

```{r}
prepped.list <- validation_prep_ordinal(raw.dat, base.dat, 'persistent_poverty')

tit <- 'Persistent Poverty'

# Now plot
ggplot(data = var, mapping = aes(x = time, y = n, group = persistent_poverty, colour = persistent_poverty)) +
  geom_line() +
  geom_vline(xintercept=start.year, linetype='dotted') +
  labs(title = tit, subtitle = 'Counts by Level') +
  xlab('Year') +
  ylab('Count')

ggplot(data = norm, mapping = aes(x = time, y = prct, fill=persistent_poverty)) +
  geom_bar(stat = 'identity') +
  geom_vline(xintercept=start.year, linetype='dotted') +
  labs(title = tit) +
  xlab('Year') +
  ylab('Proportion')

if (shall.we.save) {
  ggsave(filename = 'persistent_poverty.png',
         plot = last_plot(),
         path = save.path)
}

rm(prepped.list, var, norm, tit)

@@

### Material Deprivation

```{r}
prepped.list <- validation_prep_ordinal(raw.dat, base.dat, 'matdep_child')

tit <- 'Material Deprivation Child'

# Now plot
ggplot(data = var, mapping = aes(x = time, y = n, group = matdep_child, colour = matdep_child)) +
  geom_line() +
  geom_vline(xintercept=start.year, linetype='dotted') +
  labs(title = tit, subtitle = 'Counts by Level') +
  xlab('Year') +
  ylab('Count')

ggplot(data = norm, mapping = aes(x = time, y = prct, fill=matdep_child)) +
  geom_bar(stat = 'identity') +
  geom_vline(xintercept=start.year, linetype='dotted') +
  labs(title = tit) +
  xlab('Year') +
  ylab('Proportion')

if (shall.we.save) {
  ggsave(filename = 'matdep_child.png',
         plot = last_plot(),
         path = save.path)
}

rm(prepped.list, var, norm, tit)

```{r}
